\TitlePt

### 2016-03-16 introduction.tex
Second paragraph about the challenges of inversion

Deriving geophysical Earth models from gravity data is an inverse problem.

Designing a method for solving these inverse problems presents many challenges.

The first stage in developing an inversion method is to establish the
functional mapping between the model parameters and the data, known as the
forward problem.

For the inversion to succeed, the forward problem must be solved in a stable
and accurate way.

>>>>

Deriving geophysical Earth models from gravity data is an inverse problem.
Designing a method for solving these inverse problems presents many challenges.
The first challenge in developing an inversion method is to establish the
functional mapping between the model parameters and the data.
This is known as the forward problem.
The forward problem must be solved in a stable and accurate way for the
inversion to succeed.
The second challenge is to choose and implement an optimization algorithm to
estimate the model parameters that best fit the observed data.
There are several well established optimization methods to choose from the
literature, for example, the gradient descent Gauss-Newton method or the
stochastic Genetic Algorithm.
The optimization algorithm is problem agnostic, meaning that it does not depend
on the type of geophysical data or parametrization used.
Finally, there is the challenge of stabilizing the inverse problem.
This is often done through some form of regulatization.
Each regularizing function favors different attributes, such as smoothness or
compactness.
Choosing an appropriate regularizing function is an indirect way to include
prior geological or geophysical information.

When developing a new inversion methodology, one must implement all of the
above (forward problem, optimization, and regularization) in a software
application.
